% LaTeX sample fixture for syntax highlighting tests
\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{amsmath,amssymb}
\geometry{margin=2.2cm}

\title{GitCodeViewer Language Fixture: LaTeX}
\author{Dev Team}
\date{March 2026}

\begin{document}
\maketitle

\begin{abstract}
This document is a test fixture for language highlighting and structure rendering.
It intentionally includes sections, equations, lists, and a long table.
\end{abstract}

\section{Overview}
GitCodeViewer supports multiple language grammars through CodeMirror.
The mapping flow is extension $\rightarrow$ language ID $\rightarrow$ parser.
When one stage is missing, highlighting falls back to plain text.

\section{Design Rules}
\begin{itemize}
  \item Keep extension mappings explicit and deterministic.
  \item Add sample files for manual visual verification.
  \item Keep sample file size in a practical range.
  \item Avoid enabling unsupported UI affordances by default.
\end{itemize}

\section{Formula}
Given file score values $s_i$ with weights $w_i$:
\begin{equation}
S = \sum_{i=1}^{n} w_i \cdot s_i
\end{equation}
and normalized score:
\begin{equation}
S' = \frac{S - \min(S)}{\max(S) - \min(S)}
\end{equation}

\section{Language Table}
\begin{longtable}{lrr}
\toprule
Language & Files & Score \\
\midrule
TypeScript & 42 & 91 \\
Python & 31 & 84 \\
Rust & 18 & 79 \\
Kotlin & 15 & 74 \\
Clojure & 10 & 70 \\
Julia & 8 & 67 \\
R & 7 & 65 \\
SPARQL & 5 & 60 \\
\bottomrule
\end{longtable}

\section{Checklist}
\begin{enumerate}
  \item Update extension map.
  \item Update CodeMirror resolver switch.
  \item Add or refresh dev sample list.
  \item Keep fixtures between 80 and 200 lines.
\end{enumerate}

\section{Case Notes}
\subsection{Case 1}
Add concise and stable mappings.

\subsection{Case 2}
Route syntax IDs to maintained parser modules.

\subsection{Case 3}
Keep naming consistent: file extension, label, and language key.

\subsection{Case 4}
Prefer low-risk additions first.

\subsection{Case 5}
Track unsupported editor features per language.

\subsection{Case 6}
Avoid false-positive binary detections for text formats.

\subsection{Case 7}
Keep README and dev tools aligned to avoid confusion.

\subsection{Case 8}
Use deterministic demo content for regression checks.

\subsection{Case 9}
Confirm generated asset builds after syntax changes.

\subsection{Case 10}
Validate on device with real file opening flow.

\section{Reference}
Project page: \url{https://codemirror.net/docs/community/#language}

\section{Conclusion}
This fixture should stay readable and representative while covering common
LaTeX constructs used in technical documentation.

\end{document}

